Project-I by Group Sydney

### 2015-10-31 report/paper.tex
Add predictions

For the seventh model, the degrees of the polynomial for the clusters are $3,6$ and $3$. When we add higher degrees, we can directly observe overfitting because suddenly the training error decreases to a value near zero and the test errors grows exponentially, so with this manner we know that our degrees are not to high. The eighth model is similar to the seventh one, except that this time it uses dummy encoding and has lower degrees : $3,5$ and $2$, due to the number of input variables. We can see that feature transformations significantly improve the test error compared to other models. However, dummy encoding doesn't seem to more efficient, and so our final model will be the seventh.

@@

We analyzed a regression data set with different methods and concluded that least squares wasn't a good approach due to the ill-conditioning and the least squares gradient descent was to slow and was less efficient than ridge regression. Separation of the data into clusters was essential in order to decrease the test error. Unfortunately, dummy encoding didn't help. However using polynomial basis helped to decrease the bias. Finally, the variance of cluster 1 and 3 are very low, the one for cluster 2 is a bit higher. We think that we have bias because we use ridge regression but we don't think it is too high because we have seen that adding features helps and at a certain points it wasn't efficient. The best model we have is the seventh one, and we estimate the \textit{RMSE} of the prediction to be around $97$ with a standard deviation of $35$. Finally, we think that our model is improvable, however we couldn't try other things in order to improve the estimation error, due to a lack of time.

>>>>

For the seventh model, the degrees of the polynomial for the clusters are $3,6$ and $3$. When we add higher degrees, we can directly observe overfitting because suddenly the training error decreases to a value near zero and the test errors grows exponentially, so with this manner we know that our degrees are not to high. The eighth model is similar to the seventh one, except that this time it uses dummy encoding and has lower degrees : $3,5$ and $2$, due to the number of input variables. We can see that feature transformations significantly improve the test error compared to other models. However, dummy encoding doesn't seem to more efficient, and so our final model will be the seventh. Our final lambdas are $\lambda_1 = 0.0369, \lambda_2 = 1.8303e^{-4}$ and $\lambda_3 = 0.0053$.

@@

We analyzed a regression data set with different methods and concluded that least squares wasn't a good approach due to the ill-conditioning and the least squares gradient descent was to slow and was less efficient than ridge regression. Separation of the data into clusters was essential in order to decrease the test error. Unfortunately, dummy encoding didn't help. However using polynomial basis helped to decrease the bias. Finally, the variance of cluster 1 and 3 are very low, the one for cluster 2 is a bit higher. We think that we have bias because we use ridge regression but we don't think it is too high because we have seen that adding features helps and at a certain points it wasn't efficient. The best model we have is the seventh one, and we estimate the \textit{RMSE} of the prediction to be around $115.96$ with a standard deviation of $45.59$. Finally, we think that our model is improvable, however we couldn't try other things in order to improve the estimation error, due to a lack of time.
